analysis

### 2020-05-29 analysis.Rmd
built rarefied pxe network analysis, expanded abund/div analysis

### Define functions
```{r}
# Find breakpoints on GDD scale
breakpoints_gdd <- function(x, year, t1, t2) {

@@

# Binomial ggplot smoother
binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "quasibinomial"), se = FALSE, ...)
}

# Rare_net function: rarefies networks by iteratively subsampling more frequently sampled networks to match the transect count of the least frequently sampled one
# species level
rare_net_sp <- function(net, n, iter) {

@@

    out <- bind_rows(out, temp)
  } 
  out <- out  %>%
      gather(metric, value, -c(site, iteration)) %>% # get mean value across iterations for each metric
      group_by(site, metric) %>%
      summarize(value = mean(value)) %>%
      left_join(site_data)
}
```

@@

survey <- read_csv("./processed_data/floral_survey.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  semi_join(net, by = c("site", "plant.sp")) %>% # Consider only plants visited at a given site-date
  left_join(gdd, by = c("site", "date")) %>%
  left_join(breaks, by = c("site", "year")) %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)
```
### Floral turnover ~ elevation
```{r}
fl_sp_elev <- survey %>%
  group_by(site, plant.sp) %>%
  summarize(abund = sum(flower.cover)) %>%
  left_join(site_data) %>%
  semi_join(net, by = "plant.sp") %>%
  group_by(plant.sp) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor)

fl_sp_use_elev <- net %>%
  group_by(site, elev.mean, plant.sp) %>%
  summarize(abund = n()) %>%
  group_by(plant.sp) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor)

ggplot(fl_sp_elev, aes(elev.mean, log(abund))) +
  geom_point() +
  #geom_smooth() +
  geom_vline(aes(xintercept = elev.floor)) +
  geom_vline(aes(xintercept = elev.ceiling)) +
  facet_wrap(~reorder(plant.sp, elev.range), scales = "free_y")

ggplot(fl_sp_use_elev, aes(elev.mean, log(abund))) +
  geom_point() +
  #geom_smooth() +
  geom_vline(aes(xintercept = elev.floor)) +
  geom_vline(aes(xintercept = elev.ceiling)) +
  facet_wrap(~reorder(plant.sp, elev.range), scales = "free_y")
```

### BB density, diversity, and packing
```{r eval=FALSE, echo=FALSE}
### Per-transect Bombus density
bb_dens <- net %>%
  group_by(site, date, gdd.cum, year, elev.class2, elev.mean, break1.gdd, break2.gdd) %>%
  summarize(bb.dens = n())

### Per-transect Bombus richness
bb_rich <- net %>%
  group_by(site, date, bb.sp, gdd.cum, year, elev.class2, elev.mean, break1.gdd, break2.gdd) %>%
  summarize(bb.rich = n())

### Per-transect floral density
fl_dens <- survey %>%
  group_by(site, date, gdd.cum, year, break1.gdd, break2.gdd) %>%
  summarize(fl.dens = sum(flower.cover),
            log.fl.dens = log(sum(flower.cover)))

@@

### Join BB density and floral cover
dens_div <- bb_dens %>%
  full_join(bb_rich) %>%
  full_join(fl_dens) %>% # Note that there is not perfect alignment in site-dates between the network observations and the floral surveying, so this join will cause some NAs that will need to be removed, causing some transects to drop out of the dataset
  full_join(fl_rich) %>%
  na.omit() %>%
  ungroup %>%
  mutate(bb.per.fl = bb.dens/fl.dens,
         site = factor(site),
         yday = yday(date),
         week = week(date),
         month = month(date)) %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive")))

ggplot(dens_div, aes(log.fl.dens, bb.dens, color = year)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB density") +
  xlab("log(floral density)")

ggplot(dens_div, aes(log.fl.dens, bb.rich, color = year)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB richness") +
  xlab("log(floral density)")

ggplot(dens_div, aes(fl.rich, bb.dens, color = year)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB density") +
  xlab("Floral richness")

ggplot(dens_div, aes(fl.rich, bb.rich, color = year)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB richness") +
  xlab("Floral richness")

ggplot(dens_div, aes(fl.rich, log.fl.dens, color = year)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("log(floral density") +
  xlab("Floral richness")

ggplot(dens_div, aes(fl.rich, bb.per.fl, color = year)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB packing") +
  xlab("Florla richness")

ggplot(dens_div, aes(elev.mean, bb.per.fl)) +
  geom_point() +
  #geom_smooth(method = "lm", se = TRUE) +
  geom_smooth() +
  facet_grid(year~phase, scales = "free") +
  ylab("BB packing") +
  xlab("Elevation")

ggplot(dens_div, aes(gdd.cum, bb.per.fl)) +
  geom_point() +
  #geom_smooth(method = "lm", se = TRUE) +
  geom_smooth() +
  facet_grid(year~elev.class2, scales = "free") +
  ylab("BB packing") +
  xlab("GDD")

ggplot(dens_div, aes(gdd.cum, sqrt(bb.per.fl))) +
  geom_point() +
  #geom_smooth(method = "lm", se = TRUE) +
  geom_smooth() +
  facet_grid(elev.class2 ~ year, scales = "free") +
  ylab("BB packing") +
  xlab("GDD")

ggplot(dens_div, aes(yday, sqrt(bb.per.fl))) +
  geom_point() +
  #geom_smooth(method = "lm", se = TRUE) +
  geom_smooth() +
  facet_grid(elev.class2 ~ year, scales = "free") +
  ylab("BB packing") +
  xlab("Julian day")

ggplot(dens_div, aes(elev.mean, sqrt(bb.rich))) +
  geom_point() +
  geom_smooth() +
  facet_grid(year ~ phase)

ggplot(dens_div, aes(elev.mean, bb.dens)) +
  geom_point() +
  geom_smooth() +
  facet_grid(year ~ phase)
```

>>>>

### Define functions
#### Colony phase breakpoint functions
```{r}
# Find breakpoints on GDD scale
breakpoints_gdd <- function(x, year, t1, t2) {

@@

# Binomial ggplot smoother
binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "quasibinomial"), se = FALSE, ...)
}
```

#### Rarefied network analysis
```{r}
# Rare_net function: rarefies networks by iteratively subsampling more frequently sampled networks to match the transect count of the least frequently sampled one
# species level
rare_net_sp <- function(net, n, iter) {

@@

    out <- bind_rows(out, temp)
  } 
  out <- out  %>%
      gather(metric, value, -c(site, iteration)) %>% # get mean value across iterations for each metric
      group_by(site, metric) %>%
      summarize(value = mean(value)) %>%
      left_join(site_data)
}

# network level version 2
rare_net_nt2 <- function(net, n, iter) {

  t_filter <- net %>%
    select(site, date, phase, year) %>%
    unique() %>%
    group_by(site, phase, year) %>%
    mutate(transects = n()) %>%
    filter(transects >= n)

  for(i in 1:iter) {
    temp <- net %>%
      semi_join(t_filter) %>%
      select(site, date, phase, year) %>%
      unique() %>%
      group_by(site, phase, year) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, phase, year, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      #filter(freq > 1) %>%
      unite(webID, c(site, phase, year), sep = "_") %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(networklevel, weighted = TRUE, level = "higher",
          index = c("web asymmetry", "weighted NODF", "H2", "C score", "niche overlap", "generality")) %>% 
      data.frame() %>%
      t() %>%
      data.frame() %>%
      rownames_to_column() %>%
      dplyr::select(id = rowname, everything()) %>%
      as_tibble() %>%
      mutate(iteration = rep(i, n()))

    out <- bind_rows(out, temp)
  } 
  out <- out  %>%
      gather(metric, value, -c(id, iteration)) %>% # get mean value across iterations for each metric
      group_by(id, metric) %>%
      summarize(value = mean(value)) %>%
      separate(id, sep = "_", into = c("site", "phase", "year")) %>%
      mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
      left_join(site_data)
}

# species level version 2
rare_net_sp2 <- function(net, n, iter) {

  t_filter <- net %>%
    select(site, date, phase, year) %>%
    unique() %>%
    group_by(site, phase, year) %>%
    mutate(transects = n()) %>%
    filter(transects >= n)

  for(i in 1:iter) {
    temp <- net %>%
      semi_join(t_filter) %>%
      select(site, date, phase, year) %>%
      unique() %>%
      group_by(site, phase, year) %>%
      sample_n(n) %>%
      left_join(net) %>%
      group_by(site, phase, year, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
      summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
      #filter(freq > 1) %>%
      unite(webID, c(site, phase, year), sep = "_") %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() %>% # convert to to bipartite web
      map(specieslevel, level = "higher", index = c("d", "species strength")) %>%
      map(rownames_to_column) %>%
      map(as_tibble) %>%
      bind_rows(.id = "id") %>% # Collapse list into big data frame
      rename(sp = rowname) %>%
      mutate(iteration = rep(i, n()))

    out <- bind_rows(out, temp)
  } 
  out <- out %>%
    gather(metric, value, -c(sp, id, iteration)) %>% # get mean value across iterations for each metric
    group_by(sp, id, metric) %>%
    summarize(value = mean(value)) %>%
    separate(id, sep = "_", into = c("site", "phase", "year")) %>%
    mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
    left_join(site_data) %>%
    left_join(bb_traits, by = c("sp" = "bb.sp"))
}
```

@@

survey <- read_csv("./processed_data/floral_survey.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  #semi_join(net, by = c("site", "plant.sp")) %>% # Consider only plants visited at a given site-date
  left_join(gdd, by = c("site", "date")) %>%
  left_join(breaks, by = c("site", "year")) %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)
```
### BB and floral turnover ~ elevation
```{r}
bb_range <- net %>%
  group_by(site, elev.mean, bb.sp) %>%
  summarize(abund = n()) %>%
  group_by(bb.sp) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor,
         elev.med = elev.floor + ((elev.ceiling - elev.floor)/2))

fl_survey_elev <- survey %>%
  filter(flower.cover > 0) %>%
  group_by(site, plant.sp) %>%
  summarize(abund = sum(flower.cover)) %>%
  left_join(site_data) %>%
  semi_join(net, by = "plant.sp") %>% # constrain to plant species that were actually visited
  group_by(plant.sp) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor,
         elev.med = elev.floor + ((elev.ceiling - elev.floor)/2),
         sites = length(unique(site)))

fl_net_elev <- net %>%
  group_by(site, elev.mean, plant.sp) %>%
  summarize(abund = n()) %>%
  group_by(plant.sp) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor,
         elev.med = elev.floor + ((elev.ceiling - elev.floor)/2),
         sites = length(unique(site)))

ggplot(filter(fl_survey_elev, sites > 0), 
       aes(reorder(plant.sp, elev.med), elev.mean)) +
  geom_line(size = 1, color = "gray60") +
  geom_point(aes(size = abund), alpha = 0.5) +
  theme_bw() +
  theme(axis.text.x = element_blank())

ggplot(filter(fl_net_elev, sites > 0), 
       aes(reorder(plant.sp, elev.med), elev.mean)) +
  geom_line(size = 1, color = "gray60") +
  geom_point(aes(size = abund), alpha = 0.5) +
  theme_bw() +
  theme(axis.text.x = element_blank())

ggplot(bb_range, aes(reorder(bb.sp, elev.med), elev.mean)) +
  geom_line(size = 3, color = "gray60") +
  geom_point(aes(size = abund), alpha = 0.5) +
  theme_bw()
```

### BB abundance, diversity, and packing
```{r eval=FALSE, echo=FALSE}
### Per-transect Bombus density
bb_abund <- net %>%
  group_by(site, date, gdd.cum, year, elev.class2, 
           elev.mean, break1.gdd, break2.gdd) %>%
  summarize(bb.abund = n())

### Per-transect Bombus richness
bb_rich <- net %>%
  group_by(site, date, gdd.cum, year, elev.class2,
           elev.mean, break1.gdd, break2.gdd) %>%
  summarize(bb.rich = length(unique(bb.sp)))

### Per-transect floral abund
fl_abund <- survey %>%
  group_by(site, date, gdd.cum, year, break1.gdd, break2.gdd) %>%
  summarize(fl.abund = sum(flower.cover),
            log.fl.abund = log(sum(flower.cover)))

@@

### Join BB density and floral cover
abund_div <- bb_abund %>%
  full_join(bb_rich) %>%
  full_join(fl_abund) %>% # Note that there is not perfect alignment in site-dates between the network observations and the floral surveying, so this join will cause some NAs that will need to be removed, causing some transects to drop out of the dataset
  full_join(fl_rich) %>%
  na.omit() %>%
  ungroup %>%
  mutate(fl.per.bb = fl.abund/bb.abund,
         site = factor(site),
         yday = yday(date),
         week = week(date),
         month = month(date)) %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive")),
         total.rich = bb.rich + fl.rich,
         web.asymmetry = (bb.rich - fl.rich) / (bb.rich + fl.rich))

### BB abundance ~ floral abundance
ggplot(abund_div, aes(log.fl.abund, bb.abund, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB abundance") +
  xlab("log(floral cover)") +
  theme_bw()

### BB richness ~ floral abundance
ggplot(abund_div, aes(log.fl.abund, bb.rich, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB richness") +
  xlab("log(floral cover)") +
  theme_bw()

### BB abundance ~ floral richness
ggplot(abund_div, aes(fl.rich, bb.abund, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB abundance") +
  xlab("Floral richness")

### BB richness ~ floral richness
ggplot(abund_div, aes(fl.rich, bb.rich, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB richness") +
  xlab("Floral richness")

### Floral richness ~ floral abundance
ggplot(abund_div, aes(log.fl.abund, fl.rich, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("Floral richness") +
  xlab("log(floral cover)")

### Per-capita floral resource abundance ~ elevation
ggplot(abund_div, aes(elev.mean, log(fl.per.bb))) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  facet_grid(year~phase, scales = "free") +
  ylab("log(fl-per-bb)") +
  xlab("Elevation") +
  theme_light()

### Per-capita floral resource abundance ~ GDD
ggplot(abund_div, aes(gdd.cum, log(fl.per.bb))) +
  geom_point(alpha = 0.5, aes(color = phase)) +
  geom_smooth(color = "black", linetype = "dashed", size = 0.5) +
  facet_grid(elev.class2 ~ year, scales = "free") +
  ylab("log(fl-per-bb)") +
  xlab("GDD") +
  theme_light()

### Per-capita floral resource abundance ~ Julian day
ggplot(abund_div, aes(yday, log(fl.per.bb))) +
  geom_point(alpha = 0.5, aes(color = phase)) +
  geom_smooth(color = "black", linetype = "dashed", size = 0.5) +
  facet_grid(elev.class2 ~ year, scales = "free") +
  ylab("log(fl-per-bb)") +
  xlab("Julian day") +
  theme_light()

### BB richness ~ elevation
ggplot(abund_div, aes(elev.mean, bb.rich)) +
  geom_point() +
  geom_smooth() +
  facet_grid(year ~ phase)

### BB richness ~ GDD
ggplot(abund_div, aes(gdd.cum, bb.rich)) +
  geom_point() +
  geom_smooth() +
  facet_grid(elev.class2 ~ year)

### BB richness ~ Julian day
ggplot(abund_div, aes(yday, bb.rich)) +
  geom_point() +
  geom_smooth() +
  facet_grid(elev.class2 ~ year)

### BB abundance ~ elevation
ggplot(abund_div, aes(elev.mean, bb.abund)) +
  geom_point() +
  geom_smooth() +
  facet_grid(year ~ phase, scales = "free")

### BB abundance ~ GDD
ggplot(abund_div, aes(gdd.cum, bb.abund)) +
  geom_point() +
  geom_smooth() +
  facet_grid(elev.class2 ~ year)

### BB abundance ~ Julian day
ggplot(abund_div, aes(yday, bb.abund)) +
  geom_point() +
  geom_smooth() +
  facet_grid(elev.class2 ~ year)

### Floral richness ~ elevation
ggplot(abund_div, aes(elev.mean, fl.rich)) +
  geom_point() +
  geom_smooth() +
  facet_grid(year ~ phase)

### Floral richness ~ GDD
ggplot(abund_div, aes(gdd.cum, fl.rich)) +
  geom_point() +
  geom_smooth() +
  facet_grid(elev.class2 ~ year)

### Floral richness ~ Julian day
ggplot(abund_div, aes(yday, fl.rich)) +
  geom_point() +
  geom_smooth() +
  facet_grid(elev.class2 ~ year)

### Floral abundance ~ elevation
ggplot(abund_div, aes(elev.mean, log(fl.abund))) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  facet_grid(year ~ phase, scales = "free") +
  theme_light()

### Floral abundance ~ GDD
ggplot(abund_div, aes(gdd.cum, log(fl.abund))) +
  geom_point(aes(color = phase), alpha =  0.5) +
  geom_smooth(color = "black", linetype = "dashed", size = 0.5) +
  facet_grid(elev.class2 ~ year, scales = "free") +
  theme_light()

### Floral abundance ~ Julian day
ggplot(abund_div, aes(yday, log(fl.abund))) +
  geom_point() +
  geom_smooth() +
  facet_grid(elev.class2 ~ year)

### Total (BB = FL) richness ~ elevation
ggplot(abund_div, aes(elev.mean, total.rich)) +
  geom_point() +
  geom_smooth() +
  facet_grid(year ~ phase, scales = "free")

### Web asymmetry ~ elevation
ggplot(abund_div, aes(elev.mean, web.asymmetry)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  facet_grid(year ~ phase, scales = "free")

### Web asymmetry ~ floral abundance
ggplot(abund_div, aes(log(fl.abund), web.asymmetry)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  facet_grid(year ~ phase, scales = "free")

### Web asymmetry ~ BB abundance
ggplot(abund_div, aes(bb.abund, web.asymmetry)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  facet_grid(year ~ phase, scales = "free")

### Web asymmetry ~ Per-capita floral resource abundance
ggplot(abund_div, aes(log(fl.per.bb), web.asymmetry)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  facet_grid(year ~ phase, scales = "free")
```

### Phase x elev network analysis
```{r}
### Prepare pxe abundance and diversity table
pxe_abund_div <- abund_div %>%
  select(-gdd.cum, -yday, -week, -month, -date, -elev.class2) %>%
  gather(ad.metric, ad.value, -c(site, year, phase, elev.mean)) %>%
  group_by(site, phase, year, ad.metric) %>%
  summarize(ad.value = mean(ad.value))

pxe_net <- rare_net_nt2(net, 4, 20) %>%
  full_join((pxe_abund_div))

ggplot(filter(pxe_net, 
              metric == "H2" & ad.metric == "fl.abund"),
       aes(log(ad.value), value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, 
              metric == "H2" & ad.metric == "fl.rich"),
       aes(log(ad.value), value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, 
              metric == "H2" & ad.metric == "bb.abund"),
       aes(log(ad.value), value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, 
              metric == "H2" & ad.metric == "bb.rich"),
       aes(ad.value, value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, metric == "weighted.NODF"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, metric == "H2"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, metric == "C.score.HL"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, metric == "niche.overlap.HL"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, metric == "generality.HL"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_net, metric == "web.asymmetry"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ phase, scales = "free")

pxe_sp <- rare_net_sp2(net, 4, 20)  %>%
  full_join((pxe_abund_div))

ggplot(filter(pxe_sp, 
              metric == "d" &
                sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf", "psit") &
                ad.metric == "fl.rich"), 
       aes(ad.value, value, color = year)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(sp ~ phase, scales = "free") +
  ylim(c(0,1))

pxe_sp_mean <- pxe_sp %>%
  filter(sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf", "psit")) %>%
  group_by(site, year, phase, elev.mean, metric) %>%
  summarize(value = mean(value))

ggplot(filter(pxe_sp_mean, metric == "d"), aes(elev.mean, value)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_sp_mean, metric == "species.strength"), aes(elev.mean, value, color = metric)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ phase, scales = "free")

ggplot(filter(pxe_sp, 
              metric == "species.strength",
              sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf", "psit")), 
       aes(elev.mean, value, color = year)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(sp ~ phase, scales = "free")

ggplot(filter(pxe_sp, 
              metric == "d",
              sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf", "psit")), 
       aes(elev.mean, value, color = year)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(sp ~ phase, scales = "free") +
  ylim(c(0,1))

ggplot(filter(pxe_sp, 
              metric == "d",
              sp %in% c("bss", "hort", "pasc", "prat", "soro", "wurf", "psit")), 
       aes(elev.mean, value, color = phase)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3)) +
  facet_grid(year ~ sp, scales = "free") +
  theme_light()
```
